---
title: "Case Study"
output: github_document
---

Load key packages
```{r setup}
library(tidyverse)
library (p8105.datasets)
data(nyc_airbnb)
```

## Brainstorm Questions
* Where are the max and min airbnb prices?
  * What are average prices?
  * Where are prices going up and down?
* What's the relationship between number of reviews and average review?
* Does room type affect availability?
* What's the location of the unit?
* What areas are popular?
  * Popularity = number of units? average price?
* Are there repeat hosts?
  * If so, what does that mean?
 
Lets start coding - max and min
```{r}
max(pull(nyc_airbnb, price))
min(pull(nyc_airbnb, price))
```

Color-coded histogram showing the distribution of prices by borough
```{r}
nyc_airbnb %>%
  ggplot(aes(x = price, fill = neighbourhood_group)) +
  geom_histogram() +
  facet_grid(. ~ neighbourhood_group) +
  scale_x_continuous(limits = c(0, 250))
```

Room type availability
```{r}
plot = ggplot(data = nyc_airbnb, aes(x = room_type, y = availability_365)) +
  geom_violin()
print(plot)
```

Total reviews by borough
```{r}
number_of_reviews <- nyc_airbnb %>%
  group_by(neighbourhood_group) %>%
  summarise(total_reviews = sum(number_of_reviews, na.rm = TRUE)) %>%
  arrange(desc(total_reviews))
print(number_of_reviews)
```

```{r}
nyc_airbnb |>
  ggplot(aes(x=review_scores_location, y=price)) +
  geom_point()
```

```{r}
nyc_airbnb |>
  filter(
    neighbourhood_group == "Manhattan",
    price < 1000,
    room_type == "Entire home/apt") |>
  group_by(neighbourhood) |>
  ggplot(aes(x=lat, y=long, color=price))+
  geom_point(alpha=0.1)
```


